Summary of 2022 experiments

### 2024-10-23 code/analysis_may2024.Rmd
amount of talking trials

game_chat |> filter(chat_cond == "chat") |>
  mutate(is.chat = ifelse(words > 0, 1, 0)) %>%
  group_by(gameId, gametype) %>%
  summarize(pct_chat = mean(is.chat)) |> 
  ggplot(aes(x=reorder(gameId, pct_chat, mean), y=pct_chat, color=gametype))+geom_point()+
  theme(axis.text.x=element_blank())+
    coord_cartesian(ylim=c(0,1))
```

>>>>

game_chat |> filter(chat_cond == "chat") |>
  mutate(is.chat = ifelse(words > 0, 1, 0)) %>%
  group_by(gameId, gametype) %>%
  summarize(pct_chat = mean(is.chat)) |> 
  ggplot(aes(x=reorder(gameId, pct_chat, mean), y=pct_chat, color=gametype))+geom_point()+
  theme(axis.text.x=element_blank())+
    coord_cartesian(ylim=c(0,1))

game_chat |> filter(chat_cond == "chat") |>
  mutate(is.chat = ifelse(words > 0, 1, 0)) %>%
  group_by(gameId) %>%
  summarize(pct_chat = mean(is.chat)) |> 
  arrange(pct_chat) |> 
  mutate(x=1/n()*row_number()) |> ggplot(aes(x=x, y=pct_chat))+geom_point()+
    coord_cartesian(ylim=c(0,1))+geom_hline(yintercept=.1)+geom_hline(yintercept=.5)+labs(title="Game 4")

### 2024-10-23 code/early_expts_summary.Rmd
amount of talking trials

ggplot(when_chat, aes(x = repNum, y = pct_chat, color = cond)) +
  geom_point() +
  facet_grid(~gametype) +
  geom_smooth(se = F, method = "lm") +
  labs(y = "pct of games who said anything each round")
```
```{r}

>>>>

ggplot(when_chat, aes(x = repNum, y = pct_chat, color = cond)) +
  geom_point() +
  facet_grid(~gametype) +
  geom_smooth(se = F, method = "lm") +
  labs(y = "pct of games who said anything each round")
```

```{r}
game_chat |> filter(chat_cond == "chat") |>
  mutate(is.chat = ifelse(words > 0, 1, 0)) %>%
  mutate(game_no=str_sub(cond, -1)) |> 
  group_by(gameId, game_no) %>%
  summarize(pct_chat = mean(is.chat)) |> 
  arrange(game_no, pct_chat) |> 
  group_by(game_no) |> 
  mutate(x=1/n()*row_number()) |> ggplot(aes(x=x, y=pct_chat))+geom_point()+facet_wrap(~game_no)+
    coord_cartesian(ylim=c(0,1))+geom_hline(yintercept=.1)+geom_hline(yintercept=.5)

```
```{r}
